---
title: "Circulation Report"
header-includes:
  - \usepackage{graphicx}
  - \usepackage{fancyhdr}
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(here::here("Reports/R_Version/"), 
                        "Circulation_R.pdf"))})
output: 
  pdf_document: default
---
\fancypagestyle{plain}{
  \fancyhead[R, R]{Investigator: Dr. John Doe\\ Analyst: Grace Bosma}
  \fancyhead[L]{Project: Reproducible Report Toy Example\\ `r paste(format(Sys.Date(), '%B %d, %Y'))`}
  \setlength{\headheight}{23pt}
}

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r setup, include=FALSE}
library(tidyverse) # for piping and functions like select/filter etc
library(gtsummary) # for tabling in results
library(scales) # for p-value formatting
```

# Updates
- added some text to ReadMe.md files    
- added session info    

# Introduction

We are interested in comparing weight of vehicles with their gas mileage. We hypothesize that vehicles with a higher weight will have worse gas mileage compared to vehicles with a lower weight.

**Note this (circulation) report will only contain what is pertinent to the manuscript**

```{r import data}
# we are using mtcars 
dat_raw <- mtcars
```


# Statistical methods

A linear model including mpg as the outcome and weight (per 1000lbs) as a covariate was utilized. 

```{r adjustment}
# Using snake_case
m_linear <- lm(mpg ~ wt, data = dat_raw)
#summary(m_linear)
```

# Results

Linear model indicated that with every additional thousand pound increase in vehicle weight resulting in `r -1*round(m_linear$coefficients[2],2)` less miles per gallon (p `r scales::pvalue(summary(m_linear)$coefficients[2,4], accuracy = 0.01)`), indicating an inverse relationship between vehicle weight and gas mileage.
  
```{r table output}
gtsummary::tbl_regression(m_linear, label = wt ~ "Weight")
```


```{r Session info}
writeLines(capture.output(sessionInfo()), "circulation_session_info.txt")
```


